---
title: "fish-length-weight"
author: "Marie Rivers"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```
### Fish Length Weight
#### Created the R markdown for the last session of day 1
*I've learned a lot today*

**the website is very helpful**

* now I
 + I made a 
 + bullet list
 
 Here's a picture of Lyra
 
 ! [Alt text] (/Users/marierivers/Pictures/Lyra/2019/20191021_174201.jpq)
 
```{r}

weight_grams <- function(a, b, length_cm) {
  weight_grams = (a * (length_cm^b))
}
milkfish <- (weight_grams(a = 0.0905, b = 2.52, length_cm = 60))
print(milkfish)

trevally <- weight_grams(a = 0.0353, b = 3.05, length_cm = 60)
print(trevally)

barracuda <- weight_grams(a = 0.0181, b = 3.27, length_cm = 60)
print(barracuda)

fish_length <- seq(from = 0, to = 200, by = 1)

barracuda_weight <- weight_grams(a = 0.0181, b = 3.27, length_cm = fish_length)

barracuda_df <- data.frame(fish_length, barracuda_weight)
barracuda_df

ggplot(data = barracuda_df, aes(x = fish_length, y = barracuda_weight)) +
  geom_point() +
  labs(x = "fish length (cm)",
       y = "weight (grams)",
       title = "Barracuda Weight",
       subtitle = "barracuda weight as a function of fish length")

```
#### to use git hub, in the console, type usethis::use_git(), then answer yes, they type usethis::use_github(). There might be a more efficient way to add git with a library or something like that.

#### to upload to github, knit, select the two files, commit, add a comment, commit, pull, close, push
 
 
 